### 2016-09-18 image_setup.tex
Include Yocto reference

To get started, we first need to install an \ac{OS} that works properly
on all the \ac{Raspi} models. We will download and setup the image in
the testbed administrator \ac{PC} using a Debian-based distribution.
\todot{We could present the two methods here (Yocto vs our method).}
We
use the popular Debian-based Raspbian Linux~\cite{raspbian} given that is
the recommended and default \ac{OS} for the \ac{Raspi}. Raspbian is made
available in two bundles: Raspbian and Raspbian Lite. The difference
between the two, is that Raspbian contains a pre-installed desktop environment
for user interaction and Raspbian Lite by default only permits to interact
through a command shell. Given that the \ac{Raspi}s in our testbed are not
connected to monitors, we decide to work with Raspbian Lite.
If required, a desktop environment can be installed using the package manager later.
%\todot{remove the rest of this line} as it will be shown in the configuration section.

@@

% Define variable]
\begin{lstlisting}[]
$ export URL="https://zenodo.org/record/154328/files/"
$ export IMAGE="2016-05-27-raspbian-jessie-lite"
$ export WORKDIR="${HOME}/Raspbian"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
\todot{change to zenodo link above}

In this code block, the \texttt{\$\{URL\}} and \texttt{\$\{IMAGE\}}
variables specify where the Linux bundle is located and
\texttt{\$\{WORKDIR\}} specifies a working directory where the Raspbian
Lite bundle will be downloaded and customized. Notice that even though we
use the \$ and \# signs in the shell, in general these signs will be
particular to the testbed administrator \ac{OS} shell. Next, we create
the working directory and change to it with the \texttt{cd} command. To
download the image, we utilize the \texttt{wget} command before unpacking
the \texttt{zip} file as follows:

@@

url="http://kom.aau.dk/project/TuneSCode/raspi/"
config_file="rasp_config.zip"

>>>>

To get started, we first need to install an \ac{OS} that works properly
on all the \ac{Raspi} models. We will download and setup the image in
the testbed administrator \ac{PC} using a Debian-based distribution.
An alternative to this method, is to create a tailoared Linux distribution
for the \ac{Raspi} platform using the Yocto Project \cite{yocto}. However, this
process would require to assemble and compile all the software for the
\ac{Raspi} platform from scratch which goes beyond of the scope of our
work. We use the popular Debian-based Raspbian Linux~\cite{raspbian} given
that is the recommended and default \ac{OS} for the \ac{Raspi}. Raspbian is
made available in two bundles: Raspbian and Raspbian Lite. The difference
between the two, is that Raspbian contains a pre-installed desktop environment
for user interaction and Raspbian Lite by default only permits to interact
through a command shell. Given that the \ac{Raspi}s in our testbed are not
connected to monitors, we decide to work with Raspbian Lite.
If required, a desktop environment can be installed using the package manager later.
%\todot{remove the rest of this line} as it will be shown in the configuration section.

@@

% Define variable]
\begin{lstlisting}[]
$ export URL="https://zenodo.org/record/154328/files/"
$ export IMAGE="2016-05-27-raspbian-jessie-lite"
$ export WORKDIR="${HOME}/Raspbian"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

In this code block, the \texttt{\$\{URL\}} and \texttt{\$\{IMAGE\}}
variables specify where the Linux bundle is located and
\texttt{\$\{WORKDIR\}} specifies a working directory where the Raspbian
Lite bundle will be downloaded and customized. If the testbed administrator
allocates his / her files into another location, then it will be required to
change the \texttt{\$\{URL\}} environment variable. Notice that even though we
use the \$ and \# signs in the shell, in general these signs will be
particular to the testbed administrator \ac{OS} shell. Next, we create
the working directory and change to it with the \texttt{cd} command. To
download the image, we utilize the \texttt{wget} command before unpacking
the \texttt{zip} file as follows:

@@

url="https://zenodo.org/record/154328/files/"
config_file="rasp_config.zip"
